Catchy Part: Surveying Users' Perceptions of Threats for Wearable Devices

### 2015-01-02 wearables_survey.tex
finished the perceptions section of results (all other subsections remain).

\subsection{Perceived Concerns for Wearable Devices}
Near the end of the survey, we asked the participants an open-ended question regarding the most likely risks associated with owning and interacting with wearable devices. Without any doubt, the answers reaffirm that the most common concern for owning and interacting with wearable devices for the average user is the \textit{possible loss of privacy}:

Privacy 				464 (25.99\%) \\
Security 				94 (5.27\%)\\
Hacking 				38 (2.13\%)\\
Spying 				50 (2.80\%)\\ [-.5cm]

Unaware Use 			167 (9.36\%)\\
Accidental Sharing 		66 (3.70\%)\\
Unaware Collection		64 (3.59\%)\\
Unaware Access	 	44 (2.46\%)\\
False Information 		33 (1.85\%)\\[-.5cm]

Health Risk 			252 (14.12\%)\\
Safety 				147 (8.24\%)\\
Financial Cost	 		201 (11.26\%)\\[-.5cm]

Social Impact 			135 (7.56\%)\\
Social Stigma 			39 (2.18\%)\\
Aesthetics 			19 (1.06\%)\\[-.5cm]

Miscellaneous 		76 (4.26\%)\\
None				51 (2.86\%)\\
Don't know		 30 (1.68\%)\\
Don't care 			6 (0.34\%)\\ [-.5cm]

Other significant secondary concerns included information compromise (Security), financial cost of buying, replacing, or caring for the device (Financial), long-term health effects caused from wearing the device (Health), safety hazards from wearing the device, such as battery burns or distractions causing car accidents (Safety), and changes in social behaviors, such as dependencies on devices or spending less time with loved ones (Social Impact). Refer people to the appendix \ref{sec:coding} for detailed information on coding labels.

>>>>

\subsection{Perceived Concerns for Wearable Devices}
So far, participants had responded to questions regarding specific scenarios or assessed technologies presented to them. For completeness of the survey, we also wanted to capture the participants' general reactions to wearable devices as a whole. To do this, we asked the participants an open-ended question regarding the most likely risks associated with owning and interacting with wearable devices.

\textit{What do you think are the most likely risks associated with wearable devices?}\\[-.5cm]

This question was asked along with the demographics questions, near the end of the survey, but before any IUIPC questions regarding privacy, to avoid biasing. The participants were presented with a blank box to write in, with no character limit to their open-ended responses.

Without any doubt, the open-ended responses state that the most common concern for owning and interacting with wearable devices for the average user is the \textit{possible loss of privacy}. This top concern surpassed all other concerns by about an order of magnitude or more:

\begin{table}[h]
\begin{center}
\begin{tabular}{lll}

Concern &  Responses &  Frequency &   \\
Privacy & 452 & (25.32\%) \\
Being Unaware & 275 & (15.40\%) \\
%Unaware Use & 167 & (9.36\%)\\
%Unaware Collection & 64 & (3.59\%)\\
%Unaware Access & 44 & (2.46\%)\\
Health Risk & 191 & (10.70\%)\\
Safety & 186 & (10.42\%)\\
Financial Cost & 151 & (8.46\%)\\
Security &	144 & (8.07\%)\\
Social Impact &	157 & (8.80\%)\\
Accidental Sharing &	69 & (3.87\%)\\
Miscellaneous &	57 & (3.19\%)\\
None	& 51 & (2.86\%)\\
Social Stigma &	39 & (2.18\%)\\
False Information & 33 & (1.85\%)\\
Don't know & 31 & (1.74\%)\\
Aesthetics 	& 19 & (1.06\%)\\
Don't care 	& 11 & (0.62\%)\\

\end{tabular}
\caption{A table listing the self-reported most common risks associated with owning a wearable device.}
\label{open-responses}
\end{center}
\end{table}

Other significant secondary concerns included being unaware of what the device is collecting, doing, or which information it is using (Being Unaware), long-term health effects caused from wearing the device such as cancer from emf waves (Health), safety hazards from wearing the device such as battery burns or distractions causing car accidents (Safety), the high financial cost of buying, replacing, or caring for the device (Financial),  information compromise (Security), and resulting changes in social behaviors, such as dependencies on devices or spending less time with loved ones (Social Impact). Refer people to the appendix \ref{sec:coding} for detailed information on coding labels.
